An Improved ANS Transaction Template

### 2018-01-25 paper.tex
fix the flow
preparing pres of case3

As it is practically impossible to get reliable information about tuning a
cascade when feed with a different feed assay than the one used for its design.
Hypothesis have been made to design the response of the cascade: no physical
change are made to the different centrifuges: the cut on the machine remains the
same at every stage.

@@

\subsection{Case 2}

>>>>

As it is practically impossible to get reliable information about tuning a
cascade when feed with a different feed assay than the one used for its design.

@@

\subsection{Case 2}
The case 2 is design is also limited to 30 cascades in the scenario (limit of
the JCPOA agreement), all design the same way. In thsi case the explored design
aims to reproduce the different stage of the reference case over the different
level of cascade enrichment: the goal is to have the tails assay of a stage to
match the feed assay of the previous stage. To do so instead of aiming for a
S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w

The design properties are:\\
- less than 169 centrifuges per cascade,\\
- F/P/T assays: 0.0071/0.0296/0.002.\\% to be correct with the correct value --
                                      % this corresponds to a S/E of 5/6
The corresponding design is:\\
- 167 centrifuges,\\
- F/P/T assays: 0.0071/0.0260104/0.0019111.\\
